Closing the gap between statistical and scientific workflows for improved forecasts in ecology

### 2025-03-27 forecastflows_outline.tex
add figures in the outline

\item Divergences from this are common: 

@@

\item important question for which we cannot get data quickly, we have to use existing
\item complexity makes this simple workflow hard/impossible

@@

\item this workflow works across these realities by

@@

\item More details on ideal workflow:  walk through the different steps

@@

\item How to address current issues (two case studies)

@@

$\rightarrow$ It is a problem because we can't make decisions on +/- debate... (and it degrades trust in science?)

>>>>

\item Divergences from this are common \textbf{(Figure 1)}

@@

\item important question for which we cannot get data quickly, we have to use existing data: e.g. global datasets for trends, many various small datasets for process-based (experimental...)
\item complexity makes the ideal workflow hard/impossible

@@

\item the workflow we present here works across these realities by

@@

\item More details on ideal workflow:  walk through the different steps \textbf{(Figure 2)}

@@

\item How to address current issues (two case studies, \textbf{Figure 3})

@@

$\rightarrow$ It is a problem because we can't make decisions on +/- trends debate... (and it degrades trust in science?)
